ASHA 2023 Listening Effort Data Analysis

### 2023-10-26 ASHA 2023 Analysis/data_analysis.Rmd
Created space for describing listener demographics
This section is wip. Just loaded in the listener data for now. Will work on creating demographic tables later.

---
title: "Data Analysis"
author: "Micah E. Hirsch"
date: "2023-10-26"
output: html_document
---

@@

```{r}
summary(cars)
```

@@

```{r}
plot(pressure)
```

>>>>

---
title: "ASHA 2023 Listening Effort Data Analysis"
author: "Micah E. Hirsch"
date: "2023-10-26"
output: html_document
---

@@

# Purpose

```{r, include = F, warning = F, message = F}

# Load Needed Packages
library(rio) # install.packages("rio")
library(tidyverse) # install.packages("tidyverse")
# Need remotes package to install gazer and saccades
library(remotes) # install.packages("remotes")
library(gazer) # remotes::install_github("dmirman/gazer")
library(saccades) # remotes::install_github("tmalsburg/saccades/saccades")
library(zoo) # install.packages("zoo")
library(ggpubr)
library(gt) # install.packages("gt")

```

@@

First, we will present the demographics of our listeners To date, we recruited 20 listeners to participate in the study. Three listeners were removed from the analysis. One listener decided to withdraw from the study, so their data was removed from the database. For the other two participants, pupillometry data was either not recorded or lost due to instrumental issues. Therefore, for this analysis, we have 17 participants. The descriptive information for these participants are presented below.

```{r}

# Load in dataset for listener demographics

listener_demo <- rio::import("Cleaned Data/cleaned_listener_demo.csv")

```
